European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 manuscript/dissertation.qmd
Subtitle-fix (#1)
* comment out subtitle

* update.gitignore

* comment out subtitle in dissertation

---
title: European or American? A re-examination of the transatlantic influence over the IMF
subtitle: GV499 Dissertation
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
